Lipid Interactome Monthly Invoice

### 2025-10-31 BioinformaticsApplicationNote/ResubmissionReviewerResponse.qmd

---
format: 
  docx:
    reference-doc: custom-reference-doc.docx
---

Hello Dr. Ceci and Dr. Robinson,

We are quite excited that our manuscript is acceptable for publication and are happy to incorporate further clarifications about our data handling and the steps taken to align each dataset within the framework of the site. We are again grateful to the reviewers for taking the time to thoughtfully consider our manuscripts and the changes we incorporated in this newest version of our manuscript and our site.

We see two fundamental suggestions between the reviewers: (1) clarification of the data handling and alignment and (2) establishment of a more robust/scalable data management model.

To the first point, we have added further clarifying text to the manuscript seeking to emphasize that the data incorporated on the site is acquired through direct communication with authors -- where possible -- and from publicly available datasets published with the original studies. Further, we have added a short note on the raw data download section of the *Study Information* dropdown tab on each page to describe the source of the associated dataset (either provided by the authors or pulled from the published dataset).

We have also sought to clarify the data handling by adding a similar summary note to the s*Study Information* dropdown tab of each page describing the data wrangling performed. For most datasets, this is merely the re-naming of data columns and the inclusion of a statistical significance column which allows for color-coding in the automated plotting functions -- where "significance" is as defined in each original publication. As such, we further emphasize that direct comparison between studies is still not intended to be a quantitative method, but to give lipid researchers a sense of the similarities and differences in the sets of enriched hits between different lipid probes. A section has been added to our [Data Analysis and Statistics](https://lipidinteractome.org/background/dataanalysisandstatistics) background page describing the limitations of the comparison tool -- and this section is linked on the comparison page.

To the reviewers' second point regarding a scalable and AI-compatible data model, we wholeheartedly agree that our site's impact would be greatly increased with a more robust underlying data model. Notably, however, this first implementation of our site incorporates most, if not all, currently published lipid interactome datasets -- this is a developing field, and while interest is expanding (in part due to this effort), the scalability of the site is currently manageable via manual addition of new datasets.

We seek to emphasize that the suggested features would require root-level changes that are currently beyond our reach in both funding and skillset. We firmly aim to reconstruct the site with greater data management and a more scalable structure in its next iteration. At present, we believe that the key features of the site are of great benefit to lipid researchers: there is no comparable resource that so improves the findability and accessibility of these datasets, nor any other effort to make these datasets interoperable (as incomplete as ours is), and the downloadability of these datasets dramatically increases the reusability of these datasets.

We hope that the clarifying changes to our manuscript and the above-noted sections of our site are sufficient to address the reviewers' concerns. We thank them again for their time and consideration, and we thank the editors at Bioinformatics for this opportunity to publish our Application Note.

Best,

Dr. Fikadu Tafesse

---

**Summary of revisions**

* Clarifying text has been added to the manuscript to describe the source of datasets and the handling of data.

* Descriptive text has been added to each *Study Information* section of the site in order to clarify the source of the dataset (i.e. provided by the authors or as published/publicly available) and the steps taken to wrangle the dataset into alignment with the visualization functions on the site.

* A new section of the [Data Analysis and Statistics](https://lipidinteractome.org/background/dataanalysisandstatistics) background page clarifying the broad steps taken to align each dataset for inclusion in the site (e.g. column name alignment, the creation of a statistical annotation column, etc). This section is linked to from the dataset comparison tool to direct users who seek more information.

### 2025-10-31 Background/DataAnalysisAndStatistics.qmd
Updating with reviewer changes and some reorganization

<!-- 
## PSM quantitative mass spec analysis

* Studies included in this repository which used a PSM-based analysis pipeline
	- Hoglinger et al., 2017[@hoglingerTrifunctionalLipidProbes2017]
	- Muller et al., 2021[@mullerSynthesisCellularLabeling2021]

* Need these details. -->

@@

@@

* Gene Ontology (GO) analyses take a list of proteins and determines whether there is a greater than random enrichment of a biological feature. These features can include pathways, molecular functions, cellular compartments or biological processes. 
* In each of the GO analyses presented on this site, we filtered according to a significance cutoff -- these cutoffs are explained on the respective data pages (either "enriched candidates" or "enriched hits", as in the TMT-based datasets, or unique subsets of probe enrichment, as in the PSM-based datasets). 
* Enriched pathways are given statistical significance by assessing the likelihood that a pathway would be overrepresented through random chance.

>>>>

## Aligning datasets for presentation on this site {#sec-DataAlignment}

As described above, many methods are used to produce interactome proteomics data, and aligning these methods for interoperability ad comparison is a significant hurdle.

For numerous reasons, it is fundamentally unreasonable to quantitatively compare the results of disparate proteomics datasets -- for example, even subtle changes in instrument settings can preclude comparison of datasets collected on the same mass spectrometer and sample handling differences between individuals performing the same techniques can produce differences between very-similar datasets.

With this in mind, the Lipid Interactome seeks to align disparate datasets as much as possible and enable qualitative, visual comparisons between datasets. Each dataset is curated from its original source (either directly from the authors, or gathered from publicly available supplemental data) and wrangled to fit a standardized format, with common column headers and annotations of statistical significance.

The datasets incorporated into the [Probe vs Probe Comparison](https://lipidinteractome.org/lipidprobe/enrichedhitscomparison) tool each consist of normalized ratiometric data of fundamentally similar form, with qualitatively comparable statistical annotations.

@@

* In cases where ratiometric data is not available, heat maps have been employed to display relative enrichment between conditions. 
  * For example, [Höglinger et al. 2017](https://lipidinteractome.org/individualstudies/dh_2017) reports only peptide spectral mapping counts. In this case, we have excluded the data from the [Probe vs Probe Comparison](https://lipidinteractome.org/lipidprobe/enrichedhitscomparison) tool, as it is incompatible with this visualization technique.

@@

* **This tool is in development and is only available for some datasets.**
* Gene Ontology (GO) analyses take a list of proteins and determines whether there is a greater than random enrichment of a biological feature. These features can include pathways, molecular functions, cellular compartments or biological processes. 
* In each of the GO analyses presented on this site, we filtered according to a significance cutoff -- these cutoffs are explained on the respective data pages (either "enriched candidates" or "enriched hits", as in the TMT-based datasets, or unique subsets of probe enrichment, as in the PSM-based datasets). 
* Enriched pathways are given statistical significance by assessing the likelihood that a pathway would be overrepresented through random chance.

### Probe vs Probe Comparison tool {#sec-ProbevsProbeComparisonBackground}

* This embedded Shiny app allows the user to select two datasets to visually compare along the axes of a scatter plot.
* **Crucially, this tool is not intended for quantitative comparisons, as described in greater detail above in [@sec-DataAlignment].**
* The statistical annotations of each dataset are compared and distinguished along the axes and denoted by color: 
  * Black proteins are unenriched in respect to both probes.
  * Purple proteins are “enriched” with respect to only the probe on the x-axis.
  * Green proteins are “enriched” with respect to only the probe on the y-axis.
  * Orange proteins are “enriched” in both probes.

### 2025-10-31 BioinformaticsApplicationNote/GG_2025_applicationNote.qmd
Updating with reviewer changes and some reorganization

Where study design permits, data has been integrated into an interactive Shiny application, allowing users to perform direct (though qualitative) probe-to-probe comparisons ([Probe vs Probe Comparisons](https://www.lipidinteractome.org/lipidprobe/enrichedhitscomparison)). This tool enables researchers to explore the similarity of lipid interactomes across experimental conditions via linear regression analysis, highlighting proteins that are significantly enriched in one dataset, both datasets, or neither. By providing an intuitive framework for interactome comparison, this feature aids in the identification of promising targets for further investigation.

@@

**We wish to emphasize that we will collaborate with data providers to prepare visualizations which best suit their datasets -- the example dataset above merely depicts an ideal case which allows for easy incorporation and cross-study comparison. As proteomics techniques have improved rapidly in recent years, we have done our best to incorporate all data structures into this repository**

@@

At present, we are accepting datasets as analyzed by the original researchers, including protein identifications, enrichment quantification, and the results of statistical testing. We are working to incorporate comprehensive details of the analysis workflow in each study.

>>>>

Where study design permits, data has been integrated into an interactive Shiny application, allowing users to perform direct (though qualitative) probe-to-probe comparisons ([Probe vs Probe Comparisons](https://www.lipidinteractome.org/probevsprobecomparison/enrichedhitscomparison)). This tool enables researchers to explore the similarity of lipid interactomes across experimental conditions via linear regression analysis, highlighting proteins that are significantly enriched in one dataset, both datasets, or neither. By providing an intuitive framework for interactome comparison, this feature aids in the identification of promising targets for further investigation.

@@

**We wish to emphasize that we will collaborate with data providers to prepare visualizations which best suit their datasets -- the example dataset above merely depicts an ideal case which allows for easy incorporation and cross-study comparison. As proteomics techniques have improved rapidly in recent years, we have done our best to incorporate all data structures into this repository.**

@@

At present, we are accepting datasets as analyzed by the original researchers, including protein identifications, enrichment quantification, and the results of statistical testing. Summaries of both source and data wrangling can be found in the *Study Information* dropdown section of each data page. Further, the raw data (as provided directly by authors or pulled from publicly-available datasts) and data wrangling scripts are available for download in the same dropdown tabs.

### 2025-10-31 ContactUs/about.tex
Updating with reviewer changes and some reorganization

\begin{tcolorbox}[enhanced jigsaw, bottomrule=.15mm, opacitybacktitle=0.6, opacityback=0, coltitle=black, colframe=quarto-callout-note-color-frame, breakable, title=\textcolor{quarto-callout-note-color}{\faInfo}\hspace{0.5em}{Note}, colbacktitle=quarto-callout-note-color!10!white, colback=white, leftrule=.75mm, titlerule=0mm, bottomtitle=1mm, toptitle=1mm, arc=.35mm, rightrule=.15mm, left=2mm, toprule=.15mm]

>>>>

\begin{tcolorbox}[enhanced jigsaw, coltitle=black, colbacktitle=quarto-callout-note-color!10!white, leftrule=.75mm, colback=white, opacitybacktitle=0.6, breakable, colframe=quarto-callout-note-color-frame, rightrule=.15mm, arc=.35mm, title=\textcolor{quarto-callout-note-color}{\faInfo}\hspace{0.5em}{Note}, toptitle=1mm, opacityback=0, bottomtitle=1mm, titlerule=0mm, bottomrule=.15mm, toprule=.15mm, left=2mm]

### 2025-10-31 HourlyTracking/202508_GG-Hours.qmd
Updating with reviewer changes and some reorganization

---
title: Lipid Interactome Monthly Invoice
subtitle: August 2025
author: "Gaelen Guzman"
date: "2025 09 04"
output: 
  pdf_document:
    keep_tex: true
fontsize: 12pt
geometry: margin=1in
header-includes:
  - "\\usepackage{fancyhdr}"
  - "\\pagestyle{fancy}"
  - "\\fancyhead[L]{Gaelen Guzman}"
  - "\\fancyhead[C]{Lipid Interactome Monthly Invoice}"
  - "\\fancyhead[R]{2025 09 04}"
  - "\\fancyfoot{}"
  - "\\renewcommand{\\headrulewidth}{0.4pt}"
  - "\\renewcommand{\\footrulewidth}{0pt}"
---

>>>>

---
title: Lipid Interactome Monthly Invoice
subtitle: Invoice Number 20250801
author: "Gaelen Guzman"
date: "2025 09 04"
output: 
  pdf_document:
    keep_tex: true
fontsize: 12pt
geometry: margin=1in
header-includes:
  - "\\usepackage{fancyhdr}"
  - "\\pagestyle{fancy}"
  - "\\fancyhead[L]{Gaelen Guzman}"
  - "\\fancyhead[C]{Lipid Interactome Monthly Invoice}"
  - "\\fancyhead[R]{2025 09 04}"
  - "\\fancyhead[R]{Invoice Number 20250801}"
  - "\\fancyfoot{}"
  - "\\renewcommand{\\headrulewidth}{0.4pt}"
  - "\\renewcommand{\\footrulewidth}{0pt}"
---
